Experiment 3: Replication Analysis

### 2024-06-10 group-c/E3-analysis-replication.Rmd

confidence.t.test <- t.test(M.confidence ~ correct_recognition, data=confidence.test.data.filtered, paired=T)
```

@@

rt.t.test <- t.test(M.rt ~ correct_recognition, data=rt.test.data.filtered, paired=T)
```

>>>>

confidence.t.test <- t.test(
  confidence.test.data.filtered$M.confidence[confidence.test.data.filtered$correct_recognition == TRUE],
  confidence.test.data.filtered$M.confidence[confidence.test.data.filtered$correct_recognition == FALSE],
  paired=T)
```

@@

rt.t.test <- t.test(
  rt.test.data.filtered$M.rt[rt.test.data.filtered$correct_recognition == TRUE],
  rt.test.data.filtered$M.rt[rt.test.data.filtered$correct_recognition == FALSE],
  paired=T)
```
